---
title: "Data Wrangling Assignment(Group 6)"
author: Akshara Joshi, Ashish Gupta, Arjun J Bhatnagar,Naman Dhameja, Palak Bansal,
  Sudhanshu Ranjan
date: "20/10/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(stringr)
```
Importing Data and removing the first Row
```{r}
library(readxl)
data <- read_excel("G:/GithubBITS/Assignment3_DataWrangling/India Credit Data.xlsx", skip = 1)
View(data)
# Remove first row
data<-data[-1,]
```
Removing "End of.." Using length logic
1st Method
```{r}
# for(i in 1:range(nrow(data))){
#   if(nchar(data$`BORROWER ID`[i])>=18){
#     print(data$`BORROWER ID`[i])
#     
#     data<-data[-c(i),]
#   }
# }
```

Removing "End of.." Using Space logic
2nd method
```{r}
# for(i in 1:range(nrow(data))){
#   text = data$`BORROWER ID`[i]
#    if(str_count(text, ' ')>0){
#      data<-data[-c(i),]
#    }
# }

```
Remove columns with "End of..." using row numbers
3rd method
```{r}
# 3rd method
data<-data[-c(98,197,298,398,498,1006),]
View(data)
```

Converting different formats of string to one.

```{r}
unique(data$`Bank Account`) # Finding the unique Bank Account entries detected by the computer
tolower(unique( data$`Bank Account`))# Converting them to lowercase
trial<-data$`Bank Account` # Trial list for experimenting the operations on the column
trial<-str_replace_all(tolower(data$`Bank Account`),"-","")
unique(trial)
# Replacing similar meaning columns entered differently
data$`Bank Account`<-str_replace_all(tolower(data$`Bank Account`),"-","")
data$`Bank Account`<-replace(data$`Bank Account`,data$`Bank Account`=="dnk","do not know")

data$`Bank Account`<-replace(data$`Bank Account`,data$`Bank Account`=="nba","no bank account")
unique(data$`Bank Account`) # Again checking if now the data is cleaned or not
View(data)
```

Gender column to M,F,O only
```{r}
# Categorizing Gender Data into "Male(M)", "Female(F)", "Other(O)" 
data$Gender<-str_replace_all(tolower(data$Gender),"-","")

unique(data$Gender)
data$Gender<-replace(data$Gender,data$Gender=="male","M")
data$Gender<-replace(data$Gender,data$Gender=="m","M")

data$Gender<-replace(data$Gender,data$Gender=="female","F")
data$Gender<-replace(data$Gender,data$Gender=="f","F")

data$Gender<-replace(data$Gender,data$Gender=="other","O")
data$Gender<-replace(data$Gender,data$Gender=="o","O")

unique(data$Gender)

View(data)
```


Converting multiple NAs to "Missing"
```{r}
data$`Bank Account`[which(is.na(data$`Bank Account`))]="Missing"
data$Purpose[which(is.na(data$Purpose))]="Missing"
data$`Marital status`[which(is.na(data$`Marital status`))]="Missing"
data$SECURITY[which(is.na(data$SECURITY))]="Missing"
data$Occupation[which(is.na(data$Occupation))]="Missing"

```

Replace '-' characters in Months column
```{r}
data$Months <- str_replace_all(as.character(data$Months),"-","")
data$Age<-as.numeric(data$Age)
data$Months<-as.numeric(data$Months)

View(data)
```


Loan Closed column into Y,N only
```{r}
unique(data$`Loan Closed`)
data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="No","N")
data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="NO","N")
data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="n","N")
data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="N","N")

data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="y","Y")
data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="YES","Y")

data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="Y","Yes")
data$`Loan Closed`<-replace(data$`Loan Closed`,data$`Loan Closed`=="N","No")

unique(data$`Loan Closed`)


```
Going through the data for any discrepancies
```{r}

unique(data$Purpose)
head(data$`Loan Amount`,10)
head(data$`Annual Income`,10)
data$`Annual Income`<-as.integer(data$`Annual Income`)
```

```{r}
unique(data$`Marital status`)
data$`Marital status`<-tolower(data$`Marital status`)
unique(data$`Marital status`)
unique(data$SECURITY)
```

Creating a new column of good and bad loans, according to the purpose.
The depreciating assets are termed to be bad loans like: vehicles and repairs. 
The assets like education are considered to be good loans. 
According to this, we created 3 lists.
```{r}
trial<-c()# creating temporary empty list
unique(data$Purpose)
# Categorizing the Purpose into Good, Bad and Others
other<-list("missing","others") 
good<-list("education","business","farming")
bad<-list("household furniture/equipment","vehicle purchase  (used)","vacation" ,"domestic appliances","vehicle purchase (new)","work furniture/equipment","television","repairs" )

# Making a column according to the critera mentioned above

for( i in 1:range(nrow(data))){
  if(data$Purpose[i] %in% bad ){
    trial<-c(trial,"Bad Loan")
    
  }else if(data$Purpose[i] %in% good){
    trial<-c(trial,"Good Loan")
  }else{
    trial<-c(trial,"Missing/Other")
  }
}
data$LoanType<-trial
View(data)
summary(as.factor(data$LoanType))
```

There are few instances where all installments are paid but still loan isn't mentioned close, so for that we have changed certain entries where number of paid installments are equal to 48. 

```{r}

for( i in 1:range(nrow(data))){
  if(data$`# paid`[i]==48){
    data$`Loan Closed`[i]<-"Yes"
  }
  }
```

Calculated % paid amount and updated the %paid column in dataset. 
```{r}
View(data)
for( i in 1:range(nrow(data))){
  data$`% Paid`[i]<-round((data$`# paid`[i]/48)*100,2)
  }

```
##Potential Defaulter
Criteria decided for potential defaulter is:
1. %Paid amount is less than 40.
2. The skipped installments are atleast 30% of the number of installments paid.
```{r}
trial<-c()

for( i in 1:range(nrow(data))){
  if(data$`% Paid`[i]<=40 && data$`# skipped`[i]>=round(data$`# paid`[i]*0.3,0) ){
    trial<-c(trial,"Yes")
    
  }else{
    trial<-c(trial,"No")
  }
}
data$PotentialDefaulter<-trial
View(data)
summary(as.factor(data$PotentialDefaulter))

```
##Data Visualization

```{r}

library(ggplot2)

#potential defaulters and loan amount and purpose
ggplot(data) +
 aes(x = PotentialDefaulter, y = `Loan Amount`, fill = Purpose) +
 geom_boxplot(shape = "circle") +
 scale_fill_hue(direction = 1) +
 theme_minimal()

```

```{r}
#potential defaulters and loan amount and purpose grouped by gender
ggplot(data) +
 aes(x = PotentialDefaulter, y = `Loan Amount`, fill = Purpose) +
 geom_boxplot(shape = "circle") +
 scale_fill_hue(direction = 1) +
 theme_minimal() +
 facet_wrap(vars(Gender))
```

```{r}

library(dplyr)
library(ggplot2)
#potential defaulters and loan amount based on marital status
data %>%
 filter(!(`Marital status` %in% "missing")) %>%
 ggplot() +
 aes(x = PotentialDefaulter, y = `Loan Amount`, fill = `Marital status`) +
 geom_boxplot(shape = "circle") +
 scale_fill_hue(direction = 1) +
 theme_minimal()

```

```{r}
#loan type based on loan closed or not
data %>%
 filter(!(`Marital status` %in% "missing")) %>%
 filter(!is.na(`Loan Closed`)) %>%
 filter(!(LoanType %in% 
 "Missing/Other")) %>%
 ggplot() +
 aes(x = LoanType, y = `Loan Amount`, fill = `Loan Closed`) +
 geom_boxplot(shape = "circle") +
 scale_fill_hue(direction = 1) +
 theme_minimal()


```


